Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalogue Data

### 2013-03-04 doc/response.txt

1. The paper does not describe the resolution of the convergence maps
from the simulation.  The only number quoted is 30 arcseconds, which
(hopefully!) is not the resolution of the maps.  For example, the
convergence power spectrum peaks on arcminute scales, even neglecting
baryonic effects which only increase small-scale power. Therefore a 30
arcsecond resolution would be woefully inadequate for the purposes of
this study.  The authors should describe their simulations in more
detail, and discuss what fraction of the convergence power is
unresolved by their simulations.

# We have updated section 3.1 to state the resolution of our simulations,
and explain why it should be sufficient for our purposes.

2. My main concern about this work is that the halo occupation
distribution is assumed to be known.  As mentioned in the final
paragraph of the paper, this is a severe limitation which makes it
difficult to assess the validity of the claimed results. In reality,
uncertainties in the HOD will lead to uncertainties in the
reconstruction, and the authors should provide some estimate of these
errors.  For example, the authors could provide an example in which
the "wrong" HOD is assumed, and then compute the resulting errors in
the convergence reconstruction.  One easy example of this could be to
use the stellar masses from the Millennium catalog, which were
discarded in favor of the model of Behroozi et al.

# We agree that this is an important systematic, but we have not implemented the
suggested test. Swapping Behroozi stellar masses for the Millenium catalogue's
stellar masses is too extreme a change to be realistic - one wants to test the effect of using a wrong HOD, but where both models are within the observational limits, in light of this we have applied the Moster et al. (2010) stellar mass-halo mass relation, to generate 'true' stellar masses and reconstructed these using the Behroozi relation. The results of this investigation have been included in a new section 8.

### 2013-03-04 doc/paper-lcr.tex
small changes

\author[Collett \etal]{%
  Thomas~E.~Collett$^{1}$\thanks{\collettemail},
  Philip~J.~Marshall$^{2}$,
  Matthew~W.~Auger$^{1}$,
  Stefan~Hilbert$^{3}$,
\newauthor{%
  Sherry~H.~Suyu$^{4,3}$,
  Zachary~Greene$^{4}$,
  Tommaso~Treu$^{4}$\thanks{\packard},
  Christopher~D.~Fassnacht$^{5}$,}
\newauthor{%
  L\'eon~V.~E.~Koopmans$^{6}$,
  Maru\v{s}a Brada\v{c}$^{5}$,
  Roger~D.~Blandford$^{3}$} 
  \medskip\\
  $^1$\ioa\\
  $^2$\oxford\\
  $^3$\kipac\\
  $^4$\ucsb\\
  $^5$\davis\\
  $^6$\kapteyn
}

@@

We test the potential size of this systematic error by using the \citet{BehrooziEtal2010} relation to generate the stellar masses of our calibration lines of sight, but the stellar mass--halo mass relation of \citet{MosterEtal2010} for the ``real'' lines of sight that are reconstructed.

For halos masses of $\sim 10^{12} \Msun$ both stellar mass--halo mass relations estimate a stellar mass of $\sim 10^{10.5} \Msun$, but for halos more massive that this the stellar masses generated from the Moster relation are systematically higher than those generated from the Behroozi relation. At halo masses of $\sim 10^{14} \Msun$ the best fit stellar masses differ by $\sim 0.25$ dex.

@@

The systematic errors reported herein may be overly pessimistic; the bias is due to differences in the stellar masses predicted for high mass halos. If observations can discriminate between the high mass end of the \citet{BehrooziEtal2010} and \citet{MosterEtal2010} relations then the systematic error on the reconstruction will decrease.
}

>>>>

\author[Collett \etal]{%
  Thomas~E.~Collett$^{1}$\thanks{\collettemail},
  Philip~J.~Marshall$^{2}$,
  Matthew~W.~Auger$^{1}$,
  Stefan~Hilbert$^{3}$,
\newauthor{%
  Sherry~H.~Suyu$^{4,3,5}$,
  Zachary~Greene$^{4}$,
  Tommaso~Treu$^{4}$\thanks{\packard},
  Christopher~D.~Fassnacht$^{6}$,}
\newauthor{%
  L\'eon~V.~E.~Koopmans$^{7}$,
  Maru\v{s}a Brada\v{c}$^{6}$,
  Roger~D.~Blandford$^{3}$} 
  \medskip\\
  $^1$\ioa\\
  $^2$\oxford\\
  $^3$\kipac\\
  $^4$\ucsb\\
  $^5$\asiaa\\
  $^6$\davis\\
  $^7$\kapteyn
}

@@

It is hard to test the size of this sytematic error, since we do not know how much the real universe differs from the chosen Stellar Mass--Halo Mass relation. As wider and deeper surveys are conducted more data will become available with which to construct the Stellar Mass--Halo Mass relation; this should drive the infered Stellar Mass--Halo Mass relation closer to the truth. We are only interested in testing the effect of changing the Stellar Mass--Halo Mass relation in a way that is consistant with observational constraints; improving the observational contraints on the Stellar Mass--Halo Mass relation will decrease the the size of the systematic error on reconstructed $\kappax$ induced by assuming a specfic Stellar Mass--Halo Mass relation.

To estimate the potential size of this systematic error we use the Behroozi relation to generate the stellar masses of our calibration lines of sight, but the stellar mass--halo mass relation of Moster for the ``real'' lines of sight that are reconstructed. For halos masses of $\sim 10^{12} \Msun$ both stellar mass--halo mass relations estimate a stellar mass of $\sim 10^{10.5} \Msun$, but for halos more massive that this the stellar masses generated from the Moster relation are systematically higher than those generated from the Behroozi relation. At halo masses of $\sim 10^{14} \Msun$ the best fit stellar masses differ by $\sim 0.25$ dex.

@@

The systematic errors reported herein may be overly pessimistic; the bias is due to differences in the stellar masses predicted for high mass halos. If observations can discriminate between the high mass end of the Behroozi and Moster relations then the systematic error on the reconstruction will decrease.
}
